How to Analyze Build Logs --- A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-26 tse-paper/content.tex
Fix BibTeX

Within the past two decades, Continuous Integration (CI) has become a
ubiquitous best practice to streamline the build process of software
projects~\cite{hilton2016usage,beller2017oops,staahl2014modeling}.
Build logs are a textual by-product that automatic software build
processes create.
As a treasure trove of information~\cite{meyer},
build logs contain trace outputs of not only the elementary steps to
``make'' a project---such as retrieving and resolving dependencies and
compiling---but also about ancillary quality assurance steps---such as
testing the software and running automated static analysis tools.
The
contents of build logs can be highly variable depending on which tools
are involved in the build process and how they are
configured.
The format of logs changes as projects and build tools evolve over time.
Typically, though, they are at least a semi-structured and
somewhat stable journal of the commands executed during the build and
their results.

>>>>

In the past two decades, Continuous Integration (CI) has become a
ubiquitous best practice to streamline the build process of software
projects~\cite{hilton2016usage,beller2017oops,staahl2014modeling}.
Build logs are a textual by-product that automatic software build
processes create.
As a treasure trove of information~\cite{meyer},
build logs contain trace outputs of not only the elementary steps to
``make'' a project---such as retrieving and resolving dependencies and
compiling---but also about ancillary quality assurance steps---such as
testing the software and running automated static analysis tools.
The
contents and format of build logs can vary highly depending on which tools
are involved in the build process, how they are
configured, and as projects and build tools evolve over time~\cite{}.
Typically, though, they are at least a semi-structured and
somewhat stable journal of the commands executed during the build and
their results.
